---
title: "Senegal Data Visualization"
output: 
  flexdashboard::flex_dashboard:
        orientation: columns
        theme:
            bg: "#dbd9d9"
            fg: "#285585"
            primary: "#285585"
            base_font: !expr bslib::font_google("Lato")
        vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(shiny)
library(flexdashboard)
library(shinydashboard)
library(shinythemes)
library(shinyWidgets)
library(leaflet)
library(leaflet.extras2)
library(mapview)
library(scales)
library(dplyr)
library(htmltools)
library(ggplot2)
library(RColorBrewer)
library(fmsb)
library(psych)
library(shapefiles)
library(ggradar)
library(ggcorrplot)
library(plotly)
library(DT)
library(sf)
library(readxl)
library(yarrr)
```

```{css my-content, echo = FALSE}
a {
    color: #241678;
}
```

```{r message=FALSE}

Sys.setenv(SHAPE_RESTORE_SHX="YES")
places <- st_read("Shapefiles/zonal_stats.shp", stringsAsFactors=FALSE, quiet=TRUE)
placeBase <- read.csv("Data/Full Data.csv", sep=",", dec=".")
units <- read.csv("Data/Units.csv", sep = ",", dec = ".")
economic <- read.csv("Data/Economic.csv", sep = ",", dec = ".")
social <- read.csv("Data/Social_F.csv", sep = ",", dec = ".")
human <- read.csv("Data/Human.csv", sep = ",", dec = ".")
production <- read.csv("Data/Production.csv", sep = ",", dec = ".")
environment <- read.csv("Data/Environment.csv", sep = ",", dec = ".")
dataSource <- read_excel("Data/Variables description.xlsx")
dataWithUnits <- read.csv("Data/dataWithUnits.csv", sep = ",", dec = ".", check.names=FALSE)

```


# Instructions

## Column {data-width="700"}

### Instructions

```{r}
HTML('<iframe width="1400" height="600" src = "https://www.youtube.com/embed/A5NL0KVIw2Y" frameborder="0" allowfullscreen></iframe>')
```


# Visualization

## Inputs {.sidebar data-width="350"}

```{r warning=FALSE}
####### Map Filter

conditionalPanel(tags$style(type="text/css",
                 ".shiny-output-error { visibility: hidden; }",
                 ".shiny-output-error:before { visibility: hidden; }"),
                  condition = "input.tabselected==1",
                  uiOutput("select"),
                  uiOutput("yearmap"),
                 h6("Mean or sum of data between those years:"),
                 uiOutput("morsummap")
                )
list <- gsub("\\.", " ", names(subset(placeBase,select = -c(1,2))))
output$select <- renderUI({
  
    selectInput("select",
                   "Data you want to visualize on map:",
                   list)
  })
  
output$yearmap <- renderUI({
    
    year <- toString(names(subset(placeBase, select = c(2))))
    choice <- placeBase %>%
      group_by(Year = eval(parse(text = year)))
    minimo <- min(choice$Year)
    maximo <- max(choice$Year)
    sliderInput("yearmap",
                "Choose the mean between below years or one year:",
                min = minimo,
                max = maximo,
                value = c(minimo, maximo),
                step = 1,
                sep = "")
    
  })

output$morsummap <- renderUI({
  
  switchInput(
   inputId = "morsummap",
   value = TRUE,
   onLabel = "Mean",
   offLabel = "Sum",
   width = "400px")
  
})

```

```{r warning=FALSE}
####### SIAF Filter

conditionalPanel(condition = "input.tabselected==2",
                uiOutput("placeoryearSIAF"),
                uiOutput("selectplacesSIAF"),
                uiOutput("yearSIAF"),
                uiOutput("dataSIAF"))
                
output$placeoryearSIAF <- renderUI({
  
  selectInput("placeoryearSIAF",
               h6("Compare different districts in years or the same district in different years"),
               choices = c("Compare Districts" = "MD",
                           "Compare Years" = "SD")
  )
  
})

output$selectplacesSIAF <- renderUI({
  place <- toString(names(subset(placeBase, select = c(1))))
  choice <- placeBase %>%
    group_by(States = eval(parse(text = place)))
  
  if(input$placeoryearSIAF == "MD"){
    
    selectizeInput("selectplacesSIAF",
                   h6("Places you want to visualize on graph:"),
                   choices = c("Choose up to 10 Districts" = '',
                               choice$States),
                   multiple = TRUE,
                   options = list(maxItems = 10))
  }
  
  else if(input$placeoryearSIAF == "SD"){
    selectInput("selectplacesSIAF",
                h6("Place you want to visualize on graph:"),
                choices = c("Choose a District" = '',
                            choice$States))
  }
  
})

output$yearSIAF <- renderUI({
  
  year <- toString(names(subset(placeBase, select = c(2))))
  choice <- placeBase %>%
    group_by(Year = eval(parse(text = year)))
  minimo <- min(choice$Year)
  maximo <- max(choice$Year)
  
  if(input$placeoryearSIAF == "MD"){
    selectizeInput("yearSIAF",
                   h6("Choose years you want to compare the mean values between them"),
                   choices = c("Choose years" = '',
                               choice$Year),
                   multiple = TRUE)
  }
  else if(input$placeoryearSIAF == "SD"){
    selectizeInput("yearSIAF",
                   h6("Choose years you want to compare"),
                   choices = c("Choose years" = '',
                               choice$Year),
                   multiple = TRUE)
  }
  
})

output$dataSIAF <- renderUI({
  
  place <- toString(names(subset(placeBase, select = c(1))))
  period <- toString(names(subset(placeBase, select = c(2))))
   
  production_filtered <- production %>%
        filter(eval(parse(text = place)) %in% input$selectplacesSIAF,
               eval(parse(text = period)) %in% input$yearSIAF) %>%
        select_if(~ !any(is.na(.)))
  
  economic_filtered <- economic %>%
    filter(eval(parse(text = place)) %in% input$selectplacesSIAF,
           eval(parse(text = period)) %in% input$yearSIAF) %>%
    select_if(~ !any(is.na(.)))
  
  environment_filtered <- environment %>%
    filter(eval(parse(text = place)) %in% input$selectplacesSIAF,
           eval(parse(text = period)) %in% input$yearSIAF) %>%
    select_if(~ !any(is.na(.)))
  
  human_filtered <- human %>%
    filter(eval(parse(text = place)) %in% input$selectplacesSIAF,
           eval(parse(text = period)) %in% input$yearSIAF) %>%
    select_if(~ !any(is.na(.)))
  
  social_filtered <- social %>%
    filter(eval(parse(text = place)) %in% input$selectplacesSIAF,
           eval(parse(text = period)) %in% input$yearSIAF) %>%
    select_if(~ !any(is.na(.)))
  
  prodList <- gsub("\\.", " ", names(subset(production_filtered,select = -c(1,2))))
  econoList <- gsub("\\.", " ", names(subset(economic_filtered,select = -c(1,2))))
  socialList <- gsub("\\.", " ", names(subset(social_filtered,select = -c(1,2))))
  humanList <- gsub("\\.", " ", names(subset(human_filtered, select = -c(1,2))))
  enviroList <- gsub("\\.", " ", names(subset(environment_filtered,select = -c(1,2))))
  
  lista <- list()
  if(length(prodList)){
    lista <- append(lista, list(Production = prodList))
  }
  if(length(econoList)){
    lista <- append(lista, list(Economic = econoList))
  }
  if(length(socialList)){
    lista <- append(lista, list(Social = socialList))
  }
  if(length(humanList)){
    lista <- append(lista, list(Human = humanList))
  }
  if(length(enviroList)){
    lista <- append(lista, list(Environment = enviroList))
  }
  
  shinyWidgets::pickerInput(
    inputId = "dataSIAF",
    label = h6("Select what data you want to visualize on radar plot:"),
    choices = lista,
    multiple = TRUE)
  
})
```

```{r warning=FALSE}
####### Bar Filter

conditionalPanel(condition = "input.tabselected==3",
                uiOutput("placesBar"),
                uiOutput("yearBar"),
                h6("Mean or sum of data between those years:"),
                uiOutput("morsumbar"),
                uiOutput("dataBar")
              )

output$placesBar <- renderUI({
    place <- toString(names(subset(placeBase, select = c(1))))
    choice <- placeBase %>%
      group_by(States = eval(parse(text = place)))
    
    selectizeInput("placesBar",
                   h6("Places you want to visualize on graph:"),
                   choices = c("Choose up to 10 Districts" = '',
                             choice$States),
                   multiple = TRUE,
                   options = list(maxItems = 10))
    
  })
  
output$yearBar <- renderUI({
  
  year <- toString(names(subset(placeBase, select = c(2))))
  choice <- placeBase %>%
    group_by(Year = eval(parse(text = year)))
  minimo <- min(choice$Year)
  maximo <- max(choice$Year)
  
  sliderInput("yearBar",
              h6("Choose the years that will be ploted::"),
              min = minimo,
              max = maximo,
              value = c(minimo, maximo),
              step = 1,
              sep = "")
  
})

output$morsumbar <- renderUI({
  
  switchInput(
   inputId = "morsumbar",
   value = TRUE,
   onLabel = "Mean",
   offLabel = "Sum")
  
})

list <- gsub("\\.", " ", names(subset(placeBase,select = -c(1,2))))
output$dataBar <- renderUI({
  
  shinyWidgets::pickerInput(
    inputId = "dataBar",
    label = h6("Select what data you want to visualize on Bar plot:"),
    choices = list)
  
})

```


```{r}

# Box Filter

conditionalPanel(condition = "input.tabselected==6",
                uiOutput("placesBox"),
                uiOutput("yearBox"),
                uiOutput("dataBox")
              )

output$placesBox <- renderUI({
    place <- toString(names(subset(placeBase, select = c(1))))
    choice <- placeBase %>%
      group_by(States = eval(parse(text = place)))
    
    selectizeInput("placesBox",
                   h6("Districts you want to visualize on graph:"),
                   choices = c("Choose up to 10 Districts" = '',
                             choice$States),
                   multiple = TRUE,
                   options = list(maxItems = 10))
    
  })

output$yearBox <- renderUI({
  
  year <- toString(names(subset(placeBase, select = c(2))))
  choice <- placeBase %>%
    group_by(Year = eval(parse(text = year)))
  
  selectizeInput("yearBox",
                   h6("Choose years below which you want to visualize"),
                   choices = c("Choose your years" = '',
                               choice$Year),
                   multiple = TRUE)
  
})

list <- gsub("\\.", " ", names(subset(placeBase,select = -c(1,2))))
output$dataBox <- renderUI({
  
  shinyWidgets::pickerInput(
    inputId = "dataBox",
    label = h6("Select what data you want to visualize on Box plot:"),
    choices = list)
  
})

```

```{r warning=FALSE}
####### Correlation Filter

conditionalPanel(condition = "input.tabselected==4",
                uiOutput("placeCor"),
                uiOutput("yearCor"),
                uiOutput("dataCor")
              )

output$placeCor <- renderUI({
  
  place <- toString(names(subset(placeBase, select = c(1))))
  choice <- placeBase %>%
    group_by(States = eval(parse(text = place)))
  
  selectInput("placeCor",
              h6("Places you want to visualize on graph:"),
              choices = c("Choose one District" = '',
                          choice$States))
  
})

output$yearCor <- renderUI({
  
  year <- toString(names(subset(placeBase, select = c(2))))
  choice <- placeBase %>%
    group_by(Year = eval(parse(text = year)))
  
  selectizeInput("yearCor",
                   h6("Choose years below which you want to correlate"),
                   choices = c("Choose your years" = '',
                               choice$Year),
                   multiple = TRUE)
  
})

filterCor <- reactive({
  
  place <- toString(names(subset(placeBase, select = c(1))))
  period <- toString(names(subset(placeBase, select = c(2))))
  
  placeBase %>%
    filter(eval(parse(text = place)) %in% input$placeCor,
           eval(parse(text = period)) %in% input$yearCor) %>%
    select_if(~ !any(is.na(.)))
  
})


output$dataCor <- renderUI({
  
  list <- gsub("\\.", " ", names(subset(filterCor(),select = -c(1,2))))
  
  shinyWidgets::pickerInput(inputId = "dataCor",
                            label = h6("Select what data you want to correlate: (up to 9 variables)"),
                            choices = list,
                            multiple = TRUE,
                            options = list(maxItems = 9)
        )
  
})

```

```{r warning=FALSE}
####### Line Filter

conditionalPanel(condition = "input.tabselected==5",
                uiOutput("placesLine"),
                uiOutput("yearLine"),
                uiOutput("dataLine")
              )

output$placesLine <- renderUI({
    
  place <- toString(names(subset(placeBase, select = c(1))))
  choice <- placeBase %>%
    group_by(States = eval(parse(text = place)))
  
  selectizeInput("placesLine",
                 h6("Places you want to visualize on graph:"),
                 choices = c("Choose up to 10 Districts" = '',
                             choice$States),
                 multiple = TRUE,
                 options = list(maxItems = 10))
  
})
  
output$yearLine <- renderUI({
  
  year <- toString(names(subset(placeBase, select = c(2))))
  choice <- placeBase %>%
    group_by(Year = eval(parse(text = year)))
  minimo <- min(choice$Year)
  maximo <- max(choice$Year)
  
  sliderInput("yearLine",
              h6("Choose the years that will be ploted:"),
              min = minimo,
              max = maximo,
              value = c(minimo, maximo),
              step = 1,
              sep = "")
  
})

list <- gsub("\\.", " ", names(subset(placeBase,select = -c(1,2))))

output$dataLine <- renderUI({
  
  selectInput("dataLine",
                     h6("Select what data you want to correlate: "),
                     list)
  
})

```

## Outputs {data-width="700"}

```{r warning=FALSE}
tabsetPanel(type = "tabs",
            id = "tabselected",
            tabPanel(style = "margin: 15px",
                     "Map",
                     value=1,
                     leafletOutput("mymap",
                                  height = 600),
                      span(uiOutput("notavmap"),
                           style="text-align:center; font-weight: bold")
            ),
            tabPanel(style = "margin: 15px",
                     "SIAF",
                     value=2,
                     plotlyOutput("graphSIAF",
                                  height = 600)
            ),
            tabPanel(style = "margin: 15px",
                     "Correlation Matrix",
                     value=4,
                     plotlyOutput("graphCor",
                                  height = 600)
            ),
            tabPanel(style = "margin: 15px",
                     "Line Chart",
                     value=5,
                     plotlyOutput("graphLine",
                                  height = 600)
            ),
            tabPanel(style = "margin: 15px",
                     "Bar Chart",
                     value=3,
                     plotlyOutput("graphBar",
                                  height = 600)
            ),
            tabPanel(style = "margin: 15px",
                     "Box Chart",
                     value=6,
                     plotlyOutput("graphBox",
                                  height = 600)
            )
          )
```

```{r warning=FALSE}
####### Map Output

dataInput <- reactive({
  place <- toString(names(subset(placeBase, select = c(1))))
  period <- toString(names(subset(placeBase, select = c(2))))
  
  placeOrder <- unique(placeBase[,1])
  
  choice <- gsub("\\ ", ".", input$select)
  
  if(input$morsummap == TRUE){
    placeBase %>%
      filter(between(eval(parse(text = period)), input$yearmap[1], input$yearmap[2]))%>%
      group_by(Districts = eval(parse(text = place))) %>%
      summarise(Data = mean(eval(parse(text = choice)), na.rm=TRUE)) %>%
      arrange(factor(Districts, levels = placeOrder))
  }
  else if(input$morsummap == FALSE){
    placeBase %>%
      filter(between(eval(parse(text = period)), input$yearmap[1], input$yearmap[2]))%>%
      group_by(Districts = eval(parse(text = place))) %>%
      summarise(Data = sum(eval(parse(text = choice)), na.rm=TRUE)) %>%
      arrange(factor(Districts, levels = placeOrder))
  }
  
  
})

palette <- reactive({
  colorNumeric(c("#d7191c","#fdae61","#ffffbf","#abd9e9", "#2c7bb6"), domain = dataInput()$Data, reverse = TRUE)
})

pale <- reactive({
    colorNumeric(c("#d7191c","#fdae61","#ffffbf","#abd9e9", "#2c7bb6"), domain = dataInput()$Data)
})

labels <- reactive({
  titulo <- toString(input$select)
  unity <- units %>%
    filter(Name == titulo)
  unidade <- toString(unity$Unit)
  
  paste("<p>", dataInput()$Districts, "<p>",
        "<p>", titulo, ": ", round(dataInput()$Data, digits = 2), " ", unidade, "<p>",
        sep ="")
  
})

output$mymap <- renderLeaflet({
  
  titulo <- gsub("\\ ", ".", input$select)
  unity <- units %>%
    filter(Name == titulo)
  unidade <- toString(unity$Unit)
  
  if(!all(is.na(dataInput()$Data))){
    leaflet(width = 200, height = 300) %>%
        addTiles() %>%
        addPolygons( data = places,
                     weight = 1,
                     smoothFactor = 0.5,
                     fillOpacity = 0.8,
                     color = ~pale()(dataInput()$Data),
                     highlight = highlightOptions(
                       weight = 5,
                       color = "#666666",
                       fillOpacity = 0.7,
                       bringToFront = TRUE
                     ),
                     label = lapply(labels(), HTML)
        ) %>%
        addLegend(pal = palette(),
                  values = dataInput()$Data,
                  opacity = 0.7,
                  position = "bottomright",
                  title = unidade,
                  na.label = "n/a", 
                  labFormat = labelFormat(transform = function(x) sort(x, decreasing = TRUE)))
    }
    else if(all(is.na(dataInput()$Data))){
      leaflet(width = 200, height = 300) %>%
        addTiles() %>%
        addPolygons( data = places,
                     weight = 1,
                     smoothFactor = 0.5,
                     fillOpacity = 0.8,
                     color = "#808080",
                     highlight = highlightOptions(
                       weight = 5,
                       color = "#666666",
                       fillOpacity = 0.7,
                       bringToFront = TRUE
                     ),
                     label = lapply(labels(), HTML)
        )
    }
  
})


output$notavmap <- renderText({
  
  if(all(is.na(dataInput()$Data))){
    "No data available on this period"
  }
  
  else if(any(is.na(dataInput()$Data))){
    "n/a = No Available"
  }
})

```

```{r warning=FALSE}
####### SIAF Output

dataInputGraphSIAF <- reactive({
  place <- toString(names(subset(placeBase, select = c(1))))
  period <- toString(names(subset(placeBase, select = c(2))))
  valores <- gsub("\\ ", ".", input$dataSIAF)
  
  if(input$placeoryearSIAF == "MD"){
    
    placeBase %>%
      filter(eval(parse(text = place)) %in% input$selectplacesSIAF,
             eval(parse(text = period)) %in% input$yearSIAF) %>%
      group_by(Places = eval(parse(text = place))) %>%
      summarise_at(vars(valores), mean, na.rm=TRUE) %>%
      ungroup() %>%
      mutate_at(vars(-Places), scales::rescale)
    
  }
  
  else if(input$placeoryearSIAF == "SD"){
    
    placeBase %>%
      filter(eval(parse(text = place)) == input$selectplacesSIAF,
             eval(parse(text = period)) %in% input$yearSIAF) %>%
      group_by(Years = eval(parse(text = period))) %>%
      summarise_at(vars(valores), mean, na.rm=TRUE) %>%
      ungroup() %>%
      mutate_at(vars(-Years), scales::rescale)
    
  }
  
})

output$graphSIAF <- renderPlotly({
  
  lista <- gsub("\\.", " ", colnames(dataInputGraphSIAF())[-1])
  
  paleta <- brewer.pal(n = 8, name = "Spectral")
  paletaTransparente <- yarrr::transparent(paleta, .35)
  
  graph <-  dataInputGraphSIAF() %>%
    ggradar(
      font.radar = "roboto",
      grid.label.size = 4,
      axis.label.size = 4,
      group.point.size = 1.8,
      axis.labels = lista,
      group.colours = paletaTransparente
    ) +
    theme(
        plot.background = element_rect(fill = "#dbd9d9"),
        panel.background = element_rect(fill = "#dbd9d9"),
        legend.position = "top",
        legend.justification = c(1, 0),
        legend.text = element_text(size = 8, family = "roboto"),
        legend.key = element_rect(fill = NA, color = NA),
        legend.background = element_blank()
        )

  ggplotly(graph, tooltip = "")
  
})


  
```

```{r warning=FALSE}
####### Bar Plot

dataInputBar <- reactive({
  place <- toString(names(subset(placeBase, select = c(1))))
  period <- toString(names(subset(placeBase, select = c(2))))

  choiceG <- gsub("\\ ", ".", input$dataBar)
  if(input$morsumbar == TRUE){
    placeBase %>%
      filter(eval(parse(text = place)) %in% input$placesBar,
             between(eval(parse(text = period)), input$yearBar[1], input$yearBar[2])) %>%
      group_by(Places = eval(parse(text = place))) %>%
      summarise(Data = mean(eval(parse(text = choiceG)), na.rm=TRUE))
  }
  else if(input$morsumbar == FALSE){
    placeBase %>%
      filter(eval(parse(text = place)) %in% input$placesBar,
             between(eval(parse(text = period)), input$yearBar[1], input$yearBar[2])) %>%
      group_by(Places = eval(parse(text = place))) %>%
      summarise(Data = sum(eval(parse(text = choiceG)), na.rm=TRUE))
  }
  
  
})

output$graphBar <- renderPlotly({
  
  choiceD <- toString(input$dataBar)
  
  titulo <- gsub("\\ ", ".", input$dataBar)
  unity <- units %>%
      filter(Name == titulo)
  unidade <- toString(unity$Unit)
  
  legend <- paste(choiceD, "(", unidade, ")")
  
  barPlot <- ggplot(dataInputBar(), aes(x=Places, y=Data))+
                geom_bar(stat="identity", color="#253659", fill="#285585")+
                geom_text(aes(label=round(Data, 2)), vjust=1.6, color="#253659", size=4)+
                theme(
                  panel.background = element_rect(fill = "#dbd9d9",
                                                  colour = "#c7c7c9",
                                                  size = 0.5, linetype = "solid"),
                  plot.background = element_rect(fill = "#dbd9d9"),
                  axis.title.y = element_text(size = 8)
                )+
                labs(y = legend)+
                labs(x = "Districts")+
                scale_y_continuous(labels = comma)
  
  ggplotly(barPlot)
  
})



```

```{r}

# Box Plot

dataInputBox <- reactive({
  place <- toString(names(subset(placeBase, select = c(1))))
  period <- toString(names(subset(placeBase, select = c(2))))

  choiceG <- gsub("\\ ", ".", input$dataBox)
  
  placeBase %>%
    filter(eval(parse(text = place)) %in% input$placesBox,
           eval(parse(text = period)) %in% input$yearBox) %>%
    group_by(Places = eval(parse(text = place)))%>%
    select(Data = as.name(choiceG))
  
  
})

output$graphBox <- renderPlotly({
  
  choiceD <- toString(input$dataBox)

  titulo <- gsub("\\ ", ".", input$dataBox)
  unity <- units %>%
      filter(Name == titulo)
  unidade <- toString(unity$Unit)
  
  legend <- paste(choiceD, "(", unidade, ")")
  
  boxPlot <- ggplot(dataInputBox(), aes(x=Places, y=Data, color=Places))+
                geom_boxplot(notch=TRUE)+
                theme(
                  panel.background = element_rect(fill = "#dbd9d9",
                                                  colour = "#c7c7c9",
                                                  size = 0.5, linetype = "solid"),
                  plot.background = element_rect(fill = "#dbd9d9"),
                  axis.title.y = element_text(size = 8)
                )+
                labs(y = legend)+
        scale_y_continuous(labels = comma)
  
  ggplotly(boxPlot)
  
})



```

```{r warning=FALSE}
####### Correlation Output

dataInputCor <- reactive({
  
  
  
  place <- toString(names(subset(filterCor(), select = c(1))))
  period <- toString(names(subset(filterCor(), select = c(2))))
  choicesD <- gsub("\\ ", ".", input$dataCor)
  
  filterCor() %>%
    group_by(Places = eval(parse(text = place)))%>%
    select_at(vars(choicesD))
  
})

output$graphCor <- renderPlotly({
  
  corGraph <- dataInputCor()
  corGraph[,1] <- NULL
  colnames(corGraph) <- gsub("\\.", " ", colnames(corGraph))
  corr <- round(cor(corGraph), 1)
  
  corPlot <- ggcorrplot(corr,
                        hc.order = TRUE,
                        type = "lower",
                        lab = TRUE,
                        lab_size = 2,
                        show.diag = TRUE,
                        colors = c("red", "white","blue")) +
    theme(axis.text.x=element_text(size=9, angle=45, vjust=1, hjust=1, 
                                   margin=margin(-3,0,0,0)),
          axis.text.y=element_text(size=9),
          panel.grid.major=element_blank(),
          plot.background = element_rect(fill = "#dbd9d9"),
          panel.background = element_rect(fill = "#dbd9d9")) 
  
  ggplotly(corPlot)
  
})


```

```{r warning=FALSE}
####### Line Output

dataInputLine <- reactive({
    
  place <- toString(names(subset(placeBase, select = c(1))))
  period <- toString(names(subset(placeBase, select = c(2))))
  choicesD <- gsub("\\ ", ".", input$dataLine)
  
  placeBase %>%
    filter(eval(parse(text = place)) %in% input$placesLine,
           between(eval(parse(text = period)), input$yearLine[1], input$yearLine[2])) %>%
    group_by(Year = eval(parse(text = period)),
             Districts = eval(parse(text = place))) %>%
    select(Data = as.name(choicesD))

})

output$graphLine <- renderPlotly({
  
  choiceD <- toString(input$dataLine)
  titulo <- gsub("\\ ", ".", input$dataLine)
  unity <- units %>%
      filter(Name == titulo)
  unidade <- toString(unity$Unit)
  
  legend <- paste(choiceD, "(", unidade, ")")
  
  plotLine <- ggplot(dataInputLine(), aes(x = Year, y = Data, color = Districts)) +
    geom_line()+
    theme(panel.background = element_rect(fill = "#dbd9d9"),
          plot.background = element_rect(fill = "#dbd9d9"),
          axis.title.y = element_text(size = 8),
          legend.background = element_rect(fill = "#dbd9d9"))+
    labs(y = legend)+
    scale_x_continuous(breaks = dataInputLine()$Year)+
    scale_y_continuous(labels = comma)

  ggplotly(plotLine)
  
})



```

# Data

```{r}

h2("Data: ", style="margin: 10px;")

output$downloadData <- downloadHandler(
  filename = "SenegalDataset.csv",
  content = function(file) {write.csv(dataWithUnits, file, row.names = FALSE)}
)

renderUI({
  
  downloadButton("downloadData",
                 "Download Senegal data",
                 style="margin: 10px;")
})



DT::dataTableOutput("dataInput",
                    height = "150em")

output$dataInput <- DT::renderDataTable({dataWithUnits},options = list(pageLength = 10,
                                                                   scrollX = TRUE))

```

# About

### Description

<p style="text-align: justify; padding: 20px"> A recent study within our team (Brown et al, under review) quantified the lack of connection between the different <a href="https://sitoolkit.com/assessment-framework/the-five-domains-of-sustainable-intensification"> Sustainable Intensification Framework Domains </a> in the current and most cited research.
Therefore, we propose the design of an Integration Platform, to facilitate the visualization of interactions between the different Sustainable Intensification Framework Domain (SIAF) available data-layers.
This platform aggregates and summarizes the outcomes of our team projects and open-data sources.
This tool will serve as a Sustainable Intensification Framework application, employing Senegal as a case study, allowing the comparison between districts. </p>
<a href="https://www.siildigitalagconsortium.com/"> <h6 style="padding: 10px"> Click here to learn more about the Digital Tools, Geospatial and Farming Systems Consortium</h6></a>
<h3 style="padding: 10px"> The five domains of Sustainable Intensification: </h3>
<h5 style="padding: 10px"> Productivity: This domain is focused in everything about the land, production, productivity, outputs and inputs.</h5>
<h5 style="padding: 10px"> Economic: This is the domain related to profitability of agricultural activities and their indicators apart from land, such as: water, nutrients, labor and capital. Also, issues that may affect the probability of investment i.e. market participation are in this domain</h5>
<h5 style="padding: 10px"> Environment: Natural resources that supports agriculture (i.e. soil and water), environmental services affected by agricultural practices (i.e. habitat, water-holding capacity), and pollution which main source is agriculture (pesticides and greenhouse gases) fit in this domain. </h5>
<h5 style="padding: 10px"> Human condition: Nutrition status, food security and capacity to learn and adapt, in other words, everything that affects one individual.</h5>
<h5 style="padding: 10px"> Social: Here are the social interactions such as female participation, gender equality, ability to resolve conflicts related to agriculture and management of resources.</p>
<a href="https://sitoolkit.com/assessment-framework/the-five-domains-of-sustainable-intensification"> <h6 style="padding: 10px"> Click here to learn more about SIAF</h6></a>
<h3 style="padding: 10px"> Authors:</h3>
<p style="text-align: justify; padding: 20px">Santiago, G.; Carcedo, A. J.; Brown, M.; Grace, K.; Nejadhashemi, A.; Ciampitti, I.; Neff, J.</p>



# Data Source

```{r}
h2("Data Source: ", style="margin: 10px;")

output$downloaddataSource <- downloadHandler(
  filename = "dataSource.csv",
  content = function(file) {write.csv(dataSource, file, row.names = FALSE)}
)

renderUI({
  
  downloadButton("downloaddataSource",
                 "Download Senegal data source",
                 style="margin: 10px;")
})



DT::dataTableOutput("dataInputSource",
                    height = "150em")

output$dataInputSource <- DT::renderDataTable({dataSource},options = list(pageLength = 10,
                                                                          scrollX = TRUE))
```
